A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-01 paper.tex
update

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}

@@

In practice, It's needed to transmit raw data which has multi-parameters to clients e.g. Accelerometer, Euler Angle and Magnetometer etc. LTC not work well when we transmit multi-parameters data, cause if we just implement LTC for each parameter, the difference between estimation and origin could exceed error margin which was set in advance. For instance, there is a data $(x, y)$ with two parameters, and using LTC for both parameter respectively. According to LTC method $\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the difference between estimation and original data $(x,y)$ is which is bigger than error margin predefined. In this case, we design a new algorithm, which is multi-parameter version of LTC, and it also work with any type of distance. In standard LTC method, it checks if there is overlapping part between new sector area and recorded range. However, in our multidimensional method, we will map every data point into same time-stamp e.g. $t_0$. It is convenient for us to calculate distance between them and check if overlapping range exists. we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.
\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

>>>>

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{algpseudocode}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsthm}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\subsection{General formulation}

In this section we provide a distance-independent formulation of LTC in 
dimension $n$. The formulation of LTC in~\cite{ltc} relies on the intersection
of \emph{convex cones} in dimension $n+1$.

When $n$ is higher than 1, the intersection of convex cones unwieldy to 
formalize. Instead, we formulate LTC as an intersection test 
between $m$ \emph{balls} of dimension 
$n$. We formulate LTC recursively, as follows.

Let $x_0 \in \mathbb{R}^n$ be the last data point transmitted by the 
algorithm. For convenience, all the subsequent data points will be 
expressed in the orthogonal space with origin $x_0$. Without loss of 
generality, we assume that the data points are sampled uniformly with a 
sampling period of 1 time unit. Let k be the number of data points 
following $x_0$ that have been compressed.

The intersection of convex cones in dimension $n+1$ can be written as follows:
\ldots

Which is equivalent to the following formulation in $\mathbb{R}^n$:
\begin{eqnarray*}
&& \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
\norm{i\textbf{u} - \textbf{x}_i} \leq \epsilon\\
\Leftrightarrow && \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
\norm{\textbf{u} - \frac{1}{i}\textbf{x}_i} \leq \frac{\epsilon}{i} \\
\Leftrightarrow && \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O,
\end{eqnarray*}
where $\mathcal{B}_i 
\subset \mathbb{R}^n$ is the ball of center $\frac{1}{i}\textbf{x}_i$ 
and radius $\frac{\epsilon}{i}$.

\subsection{Effect of the norm}

It should be noted that the norm has a critical impact on the 
compression error and ratio. For instance, using the infinity instead 
of the Euclidean norm increases the compression error by a factor of 
$\sqrt{n}$ in dimension $n$, and increases the compression ratio by xxx.

%~ Point $k+1$ will be compressed if and only if:
%~ \begin{eqnarray*}
%~ && \bigcap_{i=1}^{k+1} {\mathcal{B}}_i \neq \O \\
%~ \Leftrightarrow && {\mathcal{B}}_{k+1} \cap \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O
%~ \end{eqnarray*}

\section{Implementation}
Our code is available at ... (make a clean release!)

\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
